Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-06-19 documents/TriangleScenarioArXiv/ts.tex
Removed the word Understandably

    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure. To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_structure}. Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure. The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell structure but become \textit{latent variables} in the Triangle structure. In order to embed distributions that are incompatible with the Bell structure into the Triangle structure, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$. This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome. Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}. Understandably there are numerous ways that this can be accomplished, albeit we will focus on elucidating an exemplary method.

@@

    The first inequality presented in \cref{sec:found_inequalities} was \cref{eq:ww_ineq}. \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation in \cref{fig:wagon_wheel_inflation}. The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel. The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}. These maximal as-expressible sets define a marginal scenario where the joint variables $\jointvar$ are the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
    \[ \mscenario = \AnSepExpr[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well. This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns. Understandably, this matrix is not reproduced here. The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.

@@

    Exploiting symmetries of the marginal scenario is useful for a few distinct reasons. First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:marginal_satisfiability}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope. They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope. Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not. The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is non-convex.}.

>>>>

    As was originally noticed by \citet{Fritz_2012}, it is possible to construct quantum distributions incompatible with the Triangle structure by utilizing quantum distributions incompatible with the familiar Bell structure. To explain, imagine rearranging the triangle into the configuration depicted in \cref{fig:triangle_structure_with_fritz_bell_embedded} and contrast it with the Bell structure of \cref{fig:bell_structure}. Evidently, under the correct relabeling, large portions of the Triangle structure resemble the Bell structure. The crucial distinction is that the measurement settings $S_{\p{A}}, S_{\p{B}}$ are \textit{observable variables} in the Bell structure but become \textit{latent variables} in the Triangle structure. In order to embed distributions that are incompatible with the Bell structure into the Triangle structure, the latent nodes $S_{\p{A}}, S_{\p{B}}$ need to be observable and independent of the shared latent node $\la$. This can be accomplished by having $C$ ``measure'' the measurement settings $S_{\p{A}}, S_{\p{B}}$ and announce them as an outcome. Consequently, any distribution over $\p{A}, \p{B}, S_{\p{A}}, S_{\p{B}}$ that is incompatible with Bell structure is also incompatible with the Triangle structure provided that $C$ is \textit{perfectly correlated} with $S_{\p{A}}, S_{\p{B}}$~\cite{Fritz_2012}. There are numerous ways this can be accomplished, albeit we will focus on elucidating an exemplary method.

@@

    The first inequality presented in \cref{sec:found_inequalities} was \cref{eq:ww_ineq}. \cref{eq:ww_ineq} was derived using the Wagon-Wheel inflation in \cref{fig:wagon_wheel_inflation}. The Wagon-Wheel inflation possesses $4$ copies of $C$ ($C_1, C_2, C_3, C_4$) and $2$ copies of $A$ ($A_1, A_2$) and $B$ ($B_1, B_2$) arranged in the shape of a Wagon-Wheel. The maximal as-expressible sets of the Wagon-Wheel inflation along with their ancestral dependences can be found in \cref{eq:pre_injectable_triangle_structure_wagon_wheel}. These maximal as-expressible sets define a marginal scenario where the joint variables $\jointvar$ are the set of observable nodes in the Wagon-Wheel inflation $\jointvar = \nodes'_O$:
    \[ \mscenario = \AnSepExpr[\graph]{\graph'} = \bc{\bc{A_2, B_1, C_3, C_1}, \bc{A_1, B_1, C_4, C_2}, \bc{A_1, B_2, C_1, C_3}, \bc{A_2, B_2, C_2, C_4}} \eq \label{eq:wagon_wheel_marginal_model}\]
    Given that the Fritz distribution is defined over $4$-outcomes variables, the variables in the marginal scenario are assigned $4$-outcomes as well. This marginal scenario $\mscenario$ then defines an incidence matrix $M$ capable of accommodating the Fritz distribution that has $\abs{\Events{\mscenario}} = 4 \cdot 4^{4} = 1024$ rows and $\abs{\Events{\jointvar}} = 4^8 = 65,536$ columns --- this matrix is not reproduced here. The sheer size of the incidence matrix used here makes complete solutions of the marginal problem using tools such as linear-quantifier elimination intractable.

@@

    Exploiting symmetries of the marginal scenario is useful for a few distinct reasons. First, \citet{Bancal_2010} discuss computational advantages in considering symmetric versions of marginal polytopes mentioned in \cref{sec:marginal_satisfiability}; the number of extremal points typically grows exponentially in $\jointvar$, but only polynomial for the symmetric polytope. They also note a number of interesting inequalities (such as CHSH~\cite{CHSH_Original}) can be written in a way that is symmetric under the exchange of parties, demonstrating that non-trivial inequalities can be recovered from facets of a symmetric polytope. Secondly, numerical optimizations against symmetric inequalities lead to one of two interesting cases: either the extremal distribution is symmetric itself or it is not. The latter case generates a family of incompatible distributions obtained by applying symmetry operations on the extremal distribution.\footnote{If the extremal distribution happens to be asymmetric, then one can conclude the space of accessible distributions is non-convex.}
